---
title: "About"
title-block: false
---

This website is intended as an exploratory and diagnostic dashboard for the viewing of monitoring data from the experimental site "Plantaditsch" (IT-Pla) in Caldaro sulla Strada del Vino, Bolzano, Italy. Managed by the [Tree Ecophysiology and Ecosystems](https://treeecophysiology.unibz.it/) group of the Free University of Bozen-Bolzano.

For site suggestions contact Torben Callesen at [torcallesen@unibz.it](torcallesen@unibz.it)

```{r}
#| echo: FALSE
#| output: FALSE

library(readxl)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)

user<-Sys.info()["user"]
rds_folder <- paste("C:/Users",user,"OneDrive - Scientific Network South Tyrol/Plantaditsch_repository - General/Data_dashboard/RDS_objects", sep="/") 


Vardescriptions <- read_excel(paste(rds_folder,"Vardescriptions.xlsx",sep="/"), 
    sheet = "Meteo")



```

```{r}
#| echo: FALSE
#| output: TRUE
#| title: Meteo variable descriptions

Vardescriptions %>%
  kable(
    format  = "html",    # must be html for collapse_rows to work
    digits  = 3,
    col.names = c("Figure", "Variable", "Units", "Sensor", "Datalogger", "Description")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "bordered"),
    full_width        = TRUE,
    font_size         = 13
  ) %>%
  collapse_rows(
    columns = c(1, 3, 4, 5), #columns to merge
    valign  = "middle"   # vertically centre the merged labels
  )
```